Inefficient Concessions and Mediation

### 2021-12-23 draft.tex
revise draft to submit to QJPS

\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bi}{\begin{itemize*}}
\newcommand{\ei}{\end{itemize*}}
\newcommand{\mb}{\mathbf}
\newcommand{\ve}{\varepsilon}
\newcommand{\real}{\mathbb{R}}
\newcommand{\de}{\delta}
\newcommand{\al}{\alpha}
  \usepackage{setspace}
  \onehalfspacing

@@

Equilibrium payoffs beginning from round 1 are now easily described by noting only the collective first round behavior. Let $X_{ij}$ represent the sum of discounted payoffs for country $i$ where subscripts represent first round strategies of that country. If both countries play T in round 1, the corresponding payoff to country $i$ is represented as $ X_{TT}^i=\frac {T}{1- \delta_i}$. Likewise $X_{TF}^i=({-D}+\frac{\delta_i(W-D)}{1- \delta_i} )$, $ X_{FF}^i=\frac{W-D}{1- \delta_i}$, and  $X_{FT}^i=T+W +\frac{\delta_i(W-D)}{1- \delta_i}$. $X_{FT}^h$, for example, represents payoffs for the high type of country 1 when country 1 fights and country 2 trusts in the first period. Note that because types have different discount factors, the payoffs differ by type.

@@

>>>>

\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bi}{\begin{itemize*}}
\newcommand{\ei}{\end{itemize*}}
\newcommand{\mb}{\mathbf}
\newcommand{\ve}{\varepsilon}
\newcommand{\real}{\mathbb{R}}
\newcommand{\de}{\delta}
\newcommand{\al}{\alpha}
  \usepackage{setspace}
  \doublespacing

@@

Equilibrium payoffs beginning from round 1 are now easily described by noting only the collective first round behavior.\footnote{If a parameter of the model changes after period 0, the equilibrium may be disrupted. Although it is beyond the scope of this paper, one could model this by adding a probability of equilibrium disruption followed by a new round of concessions that would essentially re-start the game--albeit with altered parameters.} Let $X_{ij}$ represent the sum of discounted payoffs for country $i$ where subscripts represent first round strategies of that country. If both countries play T in round 1, the corresponding payoff to country $i$ is represented as $ X_{TT}^i=\frac {T}{1- \delta_i}$. Likewise $X_{TF}^i=({-D}+\frac{\delta_i(W-D)}{1- \delta_i} )$, $ X_{FF}^i=\frac{W-D}{1- \delta_i}$, and  $X_{FT}^i=T+W +\frac{\delta_i(W-D)}{1- \delta_i}$. $X_{FT}^h$, for example, represents payoffs for the high type of country 1 when country 1 fights and country 2 trusts in the first period. Note that because types have different discount factors, the payoffs differ by type.

@@

One might worry about the requirement that the mediator be willing and able to ensure that the specified concessions are delivered. While it is by no means guaranteed that a mediator who will play this role exists for every conflict, it is not difficult to believe that such a mediator exists for many conflicts. We do not require a formal international enforcement mechanism, but rather that the mediator has, and is willing to use, sufficient leverage to punish a deviating party. Common examples of such punishments are financial or trade sanctions, or the withdrawal of aid or military support. Further, the mechanism can work if the mediator is either (1) only able to incentivize some portion of the concessions or (2) enforces the concessions with some probability less than 1. This would tighten the low type's incentive constraint and loosen the high type's incentive constraint, creating a different level of optimal efficiency of the concessions.\footnote{To see this, in the incentive constraints in the proof of Theorem~\ref{theorem:med}, replace $g_h$ with $q \cdot g_h$, where $q$ represents the proportion of the concession that can be enforced or the probability with which the full concession is enforced.}
